---
title: "lavaan-models-3"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r include = FALSE}
library(lavaan)
library(lavaanPlot)
library(sjPlot)
library(semPlot)
library(semTools)
library(dplyr)
library(knitr)
library(ggplot2)


# Source Functions -------------------------------------------------------------
funs <- list.files(
  here::here('code/functions'),
  full.names = TRUE
)
lapply(funs, source)

# Read data --------------------------------------------------------------------
dfm <- readr::read_rds(here::here('data', 'data-one-and-one.rds'))
```


# Unrestricted model

```{r}
fit1 <- fit_full_model(dfm, 10000, 101)
tbl1 <- model_table(
  fit1, 
  caption = "Full unrestrained model",
  file.name = "model-1-unrestricted.docx"
  )
tbl1
```

# Fully restricted model

```{r}
fit2 <- fit_restricted_model(dfm, 10000, 101)
tbl2 <- model_table(
  fit2, 
  caption = "Fully restrained model",
  file.name = "model-2-fully-restricted.docx"
  )
tbl2
```

# Main model

```{r}
fit3 <- fit_model(dfm, 10000, 101)
tbl3 <- model_table(
  fit3, 
  caption = "Partially restrained model",
  file.name = "model-3-partially-restricted.docx"
  )
tbl3
```

### Figure

```{r fig.height=6, fig.width=8}
pl <- lavaanPlot(model = fit3, 
           node_options = list(shape = "box", fontname = "Helvetica"), 
           edge_options = list(color = "grey"), 
           coefs = TRUE, sig = TRUE, covs = F, stars = "regress")

save_png(pl, here::here('results/figures', 'model-3.png'))
```


# Hypothesen

### H1

H1a: secure attachment representations in both mothers and fathers would be 
positively associated with their own sensitivity in parent-child interaction

```{r}
res_f <- boot_rho(
  data = dfm,
  x = 'V_Bindung',
  y = 'V_Sensitivity',
  n = 10000,
  method = 'pearson'
)

res_m <- boot_rho(
  data = dfm,
  x = 'M_Bindung',
  y = 'M_Sensitivity',
  n = 10000,
  method = 'pearson'
)

cat(
  paste0(
    'Father: ', res_f, '\n',
    'Mother: ', res_m
  )
)
```




H1b: higher pre- and postnatal mentalizing ability in both mothers and fathers 
would be positively associated with their own sensitivity in parent-child 
interaction  

Prenatal:
```{r}
res_f <- boot_rho(
  data = dfm,
  x = 'V_RF_AAI',
  y = 'V_Sensitivity',
  n = 10000,
  method = 'pearson'
)

res_m <- boot_rho(
  data = dfm,
  x = 'M_RF_AAI',
  y = 'M_Sensitivity',
  n = 10000,
  method = 'pearson'
)

cat(
  paste0(
    'Father: ', res_f, '\n',
    'Mother: ', res_m
  )
)
```


Postnatal:
```{r}
res_f <- boot_rho(
  data = dfm,
  x = 'V_RF_PDI',
  y = 'V_Sensitivity',
  n = 10000,
  method = 'pearson'
)

res_m <- boot_rho(
  data = dfm,
  x = 'M_RF_PDI',
  y = 'M_Sensitivity',
  n = 10000,
  method = 'pearson'
)

cat(
  paste0(
    'Father: ', res_f, '\n',
    'Mother: ', res_m
  )
)
```

### H2

```{r}
res_t1 <- boot_rho(
  data = dfm,
  x = 'V_RF_AAI',
  y = 'M_RF_AAI',
  n = 10000,
  method = 'pearson'
)

res_t2 <- boot_rho(
  data = dfm,
  x = 'M_RF_PDI',
  y = 'V_RF_PDI',
  n = 10000,
  method = 'pearson'
)

cat(
  paste0(
    'T1: ', res_t1, '\n',
    'T2: ', res_t2
  )
)
```

H2b: one partners mentalizing ability at T1 would be associated with the other 
partners mentalizing ability at T2

```{r}
res_fm <- boot_rho(
  data = dfm,
  x = 'V_RF_AAI',
  y = 'M_RF_PDI',
  n = 10000,
  method = 'pearson'
)

res_mf <- boot_rho(
  data = dfm,
  x = 'M_RF_AAI',
  y = 'V_RF_PDI',
  n = 10000,
  method = 'pearson'
)

cat(
  paste0(
    'Father T1 -> Mother T2: ', res_fm, '\n',
    'Mother T1 -> Father T2: ', res_mf
  )
)
```

H2c: one partners mentalizing ability at T2 would be associated with the other 
partners sensitivity at T2

```{r}
res_fm <- boot_rho(
  data = dfm,
  x = 'V_RF_PDI',
  y = 'M_Sensitivity',
  n = 10000,
  method = 'pearson'
)

res_mf <- boot_rho(
  data = dfm,
  x = 'M_RF_PDI',
  y = 'V_Sensitivity',
  n = 10000,
  method = 'pearson'
)

cat(
  paste0(
    'Father RF -> Mother SE: ', res_fm, '\n',
    'Mother RF -> Father SE: ', res_mf
  )
)
```

### H3

H3a: the association between one partners mentalizing ability and sensitivity 
is partially mediated by the other partners mentalizing ability 

```{r}
m <- unlist(lapply(tbl3$body$content$content$data[38,], `[[`, i = 'txt'))
f <- unlist(lapply(tbl3$body$content$content$data[37,], `[[`, i = 'txt'))

cat(
  paste0(
    'Father -> Mother -> Father: beta=', f['beta'], 
    ' b [95% CI]=', f['b [95% CI]'], ' p=', f['p'], '\n',
    'Mother -> Father -> Mother: beta=', m['beta'], 
    ' b [95% CI]=', m['b [95% CI]'], ' p=', m['p']
  )
)
```

```{r}
f <- unlist(lapply(tbl3$body$content$content$data[37,], `[[`, i = 'txt'))
m <- unlist(lapply(tbl3$body$content$content$data[38,], `[[`, i = 'txt'))

cat(
  paste0(
    'Father -> Mother -> Father: beta=', f['beta'], 
    ' b [95% CI]=', f['b [95% CI]'], ' p=', f['p'], '\n',
    'Mother -> Father -> Mother: beta=', m['beta'], 
    ' b [95% CI]=', m['b [95% CI]'], ' p=', m['p']
  )
)
```

# Add correlation matrix (with bootstrapping)

```{r}
cor_matrix(
    data = dfm, 
    nboot = 2000, 
    seed = 101, 
    file.name = 'correlation-matrix.docx'
    )
```


